---
title: "WriteUp Linear Model with prediction"
author: "Rita Jarbanda"
date: "2023-11-02"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

require(tidyverse)
require(tigerstats)
require(knitr)

data <- read.csv(file="https://onlinestatbook.com/case_studies_rvls/physical_strength/data.txt",sep="",header=TRUE)  

```

## Model 1 SIMS~ARM
### Scarttered Plot



```{r}
basicNN <- ggplot(data,aes(y=SIMS,x=ARM))

```

```{r}
basicNN + geom_point() + ggtitle("SIMS vs ARM") + theme(plot.title = element_text(hjust = 0.5, size = 20))
```


This scatter plot reflects a positive correlation since some of the dots are showing a behavior of going up diagonally. This data shows the simulation expectation of arm strength in the workers. This tells us that it is expected for most of the population to have a strength between 50 to 100 for arm strength. 

### Numerical Results

```{r}
cor(SIMS~ARM,data=data)
```


The numerical results confirmed the positive corelation of the scatter plot of SIMS vs ARM.
The larger the number we get, the larger the correlation between the two is. From this data, we can see that there is a small correspondence between the two since the number is approaching 1. 

### Inferential Results Model 1

```{r}
model.1 <- lm(SIMS~ARM,data=data)
summary.lm(model.1)
```


The equation for the line of this scenario is SIMS=0.054563xARM-4.095160. Since we have a positive coefficient, the line increases making it move from the lower left corner to the upper right corner.

### Create target

```{r}
target<-data.frame(ARM=88, GRIP=44)
```

### Predict Target Point of Model 1

```{r}
predict(model.1,target,interval=c("prediction"))
```


The table shows that our predicted target plot is 0.7063836 but 95% of the time, we are going to have a value between -1.726209 and 3.138977. 


### Scartter plot for Model 1 with linear fit

```{r}
basicNN <- ggplot(data,aes(y=SIMS,x=ARM))

```

```{r}
basicNN + geom_point() + ggtitle("SIMS vs ARM") + theme(plot.title = element_text(hjust = 0.5, size = 20)) + geom_smooth(method=lm)

```


The data above shows us the line of best fit from the data points collected from Sims vs Arms. This shows which data points are the closest to the expected results. 

## Model 2 SIMS~GRIP
### Scarttered Plot



```{r}
basicNN <- ggplot(data,aes(y=SIMS,x=GRIP))

```

```{r}
basicNN + geom_point() + ggtitle("SIMS vs GRIP") + theme(plot.title = element_text(hjust = 0.5, size = 20))
```


This scatter plot tells us the grip strength that workers need. The  plot tells us that most of the population needs to have GRIP strength between 80 and 130.  



















































































































































































